### 2009-01-24 articles/2009/geoinformatics/article.tex
a few updates
git-svn-id: https://svn.osgeo.org/qgis/trunk@10008 c8812cc2-4d05-0410-92ff-de0c093fc19c

Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS) and
an official project of the Open Source Geospatial Foundation (OSGeo). QGIS is
licensed under the GNU General Public License.

@@

\subsection{Plugins}

QGIS can be adapted to your special needs with the help of an extensible
plugin architecture. It provides libraries that can be used to create
QGIS plugins or even new applications with C++ or Python. Most Python plugins
are managed in external repositories, and can be easily installed using the
Python Plugin Installer.

>>>>

Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS) and
an official project of the Open Source Geospatial Foundation (OSGeo). QGIS is
written in C++ and Python with a QT based GUI. It is licensed inder the GNU
General Public License (GPL).

@@

\subsection{Plugin Architecture}

QGIS can be customized to your special needs with the help of an extensible
plugin architecture. It provides libraries that can be used to create
QGIS plugins or even new applications with C++ or Python.

\subsection{External Python Plugin Repositories}

Most Python plugins are managed in external repositories, and can be easily
installed using the Python Plugin Installer.
